### 2022-11-26 ms.rmd
OK, we've got a no phylo model too so that we can be sure phylogeny makes a difference

saveRDS(mcmcglmm_model, file = "./output/model/mcmcglmm_model")
saveRDS(mcmcglmm_model_z_trans, file = "./output/model/mcmcglmm_model_z_trans")
} else{
  mcmcglmm_model <- readRDS("./output/model/mcmcglmm_model")
}

>>>>

# Ditch phylogeny to see if there is support for including it or not. DIC is WAY lower for phylogenetic model, so good to include it.
prior2 = list(R = list(V = diag(3), nu=1.002))
mcmcglmm_model_z_trans_nophylo <- MCMCglmm::MCMCglmm(cbind(z_ctmax, z_cfts, z_tdt_z) ~ -1 + trait, rcov = ~us(trait):units, pedigree=tree3,burnin=1000, nitt = 300000, thin = 5, family = rep("gaussian", 3), prior = prior2, pl = TRUE, pr = TRUE, data = data)

saveRDS(mcmcglmm_model, file = "./output/model/mcmcglmm_model")
saveRDS(mcmcglmm_model_z_trans, file = "./output/model/mcmcglmm_model_z_trans")
saveRDS(mcmcglmm_model_z_trans_nophylo, file = "./output/model/mcmcglmm_model_z_trans_nophylo")
} else{
  mcmcglmm_model <- readRDS("./output/model/mcmcglmm_model")
  mcmcglmm_model_z_trans <- readRDS("./output/model/mcmcglmm_model_z_trans")
mcmcglmm_model_z_trans_nophylo <- readRDS("./output/model/mcmcglmm_model_z_trans_nophylo")
}
